Tor's Usability for Censorship Circumvention

### 2015-04-16 PETS2015-paper/paper.tex
Fewer dots.

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item {\bfseries Targeting specific pluggable transports.}
Some pluggable transports work in censorship environments
where others do not.
Additionally, some of them require additional information
(like bridge addresses) before they work.
Is there a way to target testing of specific transports?
Is there anything to infer from participants' selection of transports, 
or do we assume they are trying transports at random?

\item {\bfseries Censorship environments.}
Our proposed censorship environments are informed
by real-world censors.
What other representative environments
should be tested?

\item {\bfseries Browsing tasks.}
Circumvention is broader than the stereotypical
``dissident blogger'' use case.
We have invented some tasks that use some of the
most popular web sites.
What other browsing tasks make sense to test?

\item {\bfseries Experimental design.}
Our initial study was aimed at a specific subset of users (journalists).
We plan to remove this restriction in order
to have a larger participant population.
We aim to make our results reproducible by publishing
our software and firewall configurations.
\end{itemize}

>>>>

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item {\bfseries Targeting specific pluggable transports}
Some pluggable transports work in censorship environments
where others do not.
Additionally, some of them require additional information
(like bridge addresses) before they work.
Is there a way to target testing of specific transports?
Is there anything to infer from participants' selection of transports, 
or do we assume they are trying transports at random?

\item {\bfseries Censorship environments}
Our proposed censorship environments are informed
by real-world censors.
What other representative environments
should be tested?

\item {\bfseries Browsing tasks}
Circumvention is broader than the stereotypical
``dissident blogger'' use case.
We have invented some tasks that use some of the
most popular web sites.
What other browsing tasks make sense to test?

\item {\bfseries Experimental design}
Our initial study was aimed at a specific subset of users (journalists).
We plan to remove this restriction in order
to have a larger participant population.
We aim to make our results reproducible by publishing
our software and firewall configurations.
\end{itemize}
